%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Published}
%---------------------------------------------------------

\begin{cvpubs} 
    \cvpub{\textbf{Nico Catalano}, Monica Leone, and Matteo Matteucci. \\
    Tackling Environmental Variability: Few Shot Segmentation for Domain-Adaptive Weed Segmentation in Agricultural Robotics. \\
    In \textit{International Conference on Automation Science and Engineering (CASE 2024)}, 2024.}
    
    \cvpub{\textbf{Nico Catalano}, Alessandro Maranelli, Agnese Chiatti, and Matteo Matteucci. \\
    More than the Sum of Its Parts: Ensembling Backbone Networks for Few-Shot Segmentation. \\
    In \textit{International Joint Conference on Neural Networks (IJCNN)}, 2024.}
   


    \cvpub{Riccardo Bertoglio, Alessio Mazzucchelli, \textbf{Nico Catalano}, and Matteo Matteucci. \\
    A comparative study of Fourier transform and CycleGAN as domain adaptation techniques for weed segmentation. \\
    \textit{Smart Agricultural Technology}, vol. 4, pp. 100188, 2023.}
    

    
    \cvpub{Agnese Chiatti, Riccardo Bertoglio, \textbf{Nico Catalano},Matteo Gatti, and  Matteo Matteucci. \\
    Surgical fine-tuning for Grape Bunch Segmentation under Visual Domain Shifts. \\
    In \textit{2023 European Conference on Mobile Robots (ECMR)}, pp. 1--7. IEEE, 2023.}
    


    
\end{cvpubs}

% %---------------------------------------------------------
\cvsubsection{In Review}
% %---------------------------------------------------------

\begin{cvpubs}
    % \cvpub{\textbf{Nico Catalano}, and Matteo Matteucci. \\
    % Few Shot Semantic Segmentation: a review of methodologies, benchmarks, and open challenges. \\
    % \textit{ACM Computing Surveys}}
    
    \cvpub{\textbf{Nico Catalano}, Sofia Matilde Luglio, Agnese Chiatti, Mino Sportelli, Christian Frasconi, Davide Facchinetti, Matteo Matteucci.\\
    Balancing Accuracy and Cost in Precision Agriculture: a Few-Shot Learning Approach for Effictien Weed - Crop Segmentation. \\
    in \textit{Computer and Electronics in Agriculture}}

    \cvpub{Marius Aasan, Martine Hjelkrem-Tan, \textbf{Nico Catalano}, Changkyu Choi, Ad\'in Ram\'irez~Rivera.\\
    Differentiable Hierarchical Tokenization for Vision Transformers \\
    in \textit{Conference on Computer Vision and Pattern Recognition}}
\end{cvpubs}

